Draft-assinment1

### 2017-02-15 Draft-xuezhou-sjb.Rmd
Update Draft-xuezhou-sjb.Rmd

#Table of Contents
* 1.Introduction
* 2.Goal
* 3.Dataset Preparation
* 4.Objective
* 5.Summary of variables
 * 5.1 Individual variable summary
  * 5.1.1 School
   * 5.1.1.1 State
   * 5.1.1.2 Predominant Degree
   * 5.1.1.3 Control of Institution
  * 5.1.2 Student Body
    * 5.1.2.1 Percentage first-generation students
    * 5.1.2.2 Number of applications
  * 5.1.3 Cost 
    * 5.1.3.1 Average net price for Title IV institutions(both public and private institutions)
    * 5.1.3.2 Percentage of students who are financially independent
  * 5.1.4 Financial Aid
    * 5.1.4.1 Percentage of undergraduates who receive a Pell Grant
    * 5.1.4.2 Percent of all federal undergraduate students receiving a federal student loan
    * 5.1.4.3 The median debt for students who have completed
    * 5.1.4.4 The median debt for students who have not completed
  * 5.1.5 Earning
    * 5.1.5.1 Median family income in real 2015 dollars
    * 5.1.5.2 Earning after graduation
  * 5.1.6 Repayment
    * 5.1.6.1 3-year Repayment rate
    * 5.1.6.2 3-year Default rate
* 6.Relationship between variables
 * 6.1 NPT4_COMBINE VS State
 * 6.2 Debt VS Cost
 * 6.3 Percentage of Pell Grant VS college type(CONTROL)
 * 6.4 Percentage first-generation students VS Statu
 * 6.5 family income with Pell Grant
 * 6.6 cost and median debts with earning
 * 6.7 default with earning
 * 6.8 degree type vs. earning
 * 6.9 predominant degree, control  and earning after 6 year of entry
 * 6.10 predominant degree + control (count)
 * 6.11 control + earning
* 7. Comparison between variables
* 8. Findings and Conclusion

#1. Introduction
The College Scorecard project is designed to increase the transparency of the college data, working as a navigator for students to make informed decisions about their choice for higher education. The information gathered in the dataset also gives students and families more power to differentiate postsecondary institutions and get an idea about how well colleges are preparing their students to be successful. The dataset is created to address the lack of information about college costs, earnings, federal student aid, admission rate etc. The data provides insights into the performance of institutions that receive federal aid dollars, and the outcomes of the students of those institutions. It also gives extra support for students and families to weight the tradeoffs on choosing the right college according to their own needs and educational goals.

>>>>

#Table of Contents
* 1.[Introduction](#Introduction)
* 2.Goal
* 3.Dataset Preparation
* 4.Objective
* 5.Summary of variables
 * 5.1 Individual variable summary
  * 5.1.1 School
    * 5.1.1.1 State
    * 5.1.1.2 Predominant Degree
    * 5.1.1.3 Control of Institution
  * 5.1.2 Student Body
    * 5.1.2.1 Percentage first-generation students
    * 5.1.2.2 Number of applications
  * 5.1.3 Cost 
    * 5.1.3.1 Average net price for Title IV institutions(both public and private institutions)
    * 5.1.3.2 Percentage of students who are financially independent
  * 5.1.4 Financial Aid
    * 5.1.4.1 Percentage of undergraduates who receive a Pell Grant
    * 5.1.4.2 Percent of all federal undergraduate students receiving a federal student loan
    * 5.1.4.3 The median debt for students who have completed
    * 5.1.4.4 The median debt for students who have not completed
  * 5.1.5 Earning
    * 5.1.5.1 Median family income in real 2015 dollars
    * 5.1.5.2 Earning after graduation
  * 5.1.6 Repayment
    * 5.1.6.1 3-year Repayment rate
    * 5.1.6.2 3-year Default rate
* 6.Relationship between variables
 * 6.1 NPT4_COMBINE VS State
 * 6.2 Debt VS Cost
 * 6.3 Percentage of Pell Grant VS college type(CONTROL)
 * 6.4 Percentage first-generation students VS Statu
 * 6.5 family income with Pell Grant
 * 6.6 cost and median debts with earning
 * 6.7 default with earning
 * 6.8 degree type vs. earning
 * 6.9 predominant degree, control  and earning after 6 year of entry
 * 6.10 predominant degree + control (count)
 * 6.11 control + earning
* 7. Comparison between variables
* 8. Findings and Conclusion

#1. Introduction<a id="Introduction"></a>
The College Scorecard project is designed to increase the transparency of the college data, working as a navigator for students to make informed decisions about their choice for higher education. The information gathered in the dataset also gives students and families more power to differentiate postsecondary institutions and get an idea about how well colleges are preparing their students to be successful. The dataset is created to address the lack of information about college costs, earnings, federal student aid, admission rate etc. The data provides insights into the performance of institutions that receive federal aid dollars, and the outcomes of the students of those institutions. It also gives extra support for students and families to weight the tradeoffs on choosing the right college according to their own needs and educational goals.
